---
title: "Reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{reference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(iomath)
```

## Output

### Conversion to `tex`

```{r}
e <- Ryacas::ysym("((2*Sin(2+x))^2 + (a+b)^2)^3")
e
o <- Ryacas::tex(e)
o
```

$$
`r o`
$$

All as hard brackets:

```{r}
o2 <- hbtex(e)
o2
```

$$
`r o2`
$$

Customised bracketing:

```{r}
o3 <- btex(e)
o3
```

$$
`r o3`
$$

An argument specifying `brackets` can be given (recycled):

```{r}
o4 <- btex(e, 
           brackets = list(
             c("\\langle", "\\rangle"),
             c("\\{", "\\}")))
o4
```

$$
`r o4`
$$


## Input

### Assumptions

* Variables are single letters: a-z, A-Z (e.g. $x$, $y$, $a$, $b$)
  + This has been done to better interpret user-input such as `2x` to mean `2*x`

### Implicit product

```{r}
make_products_explicit("2x")
make_products_explicit("2(1+2)")
make_products_explicit("x(y)")
make_products_explicit("(1+2)3") # Not allowed by definition
make_products_explicit("(1+2)x") # Is allowed
make_products_explicit("x(2+1) + sin(y)")
make_products_explicit("sin(2+1) + x(y+1)")
make_products_explicit("(2x)(y+1)")
```

By default, the allowed functions are those of `getGroupMembers("Math")`:

```{r}
getGroupMembers("Math")
```

This can be changed:

```{r}
make_products_explicit("sin(1) + cos(1)", allowed_functions = c('cos'))
```


### Safe evaluation

By default, safe evaluation inserts inner products.

```{r}
safe_eval("2.2", vars = NULL)
safe_eval("2.2x^2", vars = list(x = 0.2))
safe_eval("2.2*x^2", vars = list(x = 0.2))
safe_eval("2,2*x^2", vars = list(x = 0.2))
```

Efterything after first `;` is ignored:

```{r}
safe_eval("1; 2; 3")
```

#### Disallowed inputs

```{r, error = TRUE}
safe_eval("print(2)")
```

### Comparing

```{r}
grd <- expand.grid(x = seq(-10, 10, length.out = 10))
answer <- Ryacas::ysym("2*x^2")
compare_reply_answer(reply = "2x^2", 
                     answer = answer, 
                     compare_grid = grd)
compare_reply_answer(reply = "2.3x^2", 
                     answer = answer, 
                     compare_grid = grd)
```

```{r}
m <- matrix(c("2+z^3", "2*sin(x)", "3*y^2", "1.1*x^2"), 2, 2)
m
ans <- Ryacas::ysym(m)
ans
grd <- expand.grid(x = seq(-10, 10, length.out = 5),
                   y = seq(-10, 10, length.out = 5),
                   z = seq(-10, 10, length.out = 5))
compare_reply_answer(reply = m, 
                     answer = ans, 
                     compare_grid = grd)
compare_reply_answer(reply = m[1, 1], 
                     answer = ans, 
                     compare_grid = grd)
m2 <- apply(m, 2, paste0, '+0.1')
m2
compare_reply_answer(reply = m2, 
                     answer = ans, 
                     compare_grid = grd)
```



